---
title: "Analytics Implementation Scorecard"
author: "Max G"
date: "Tuesday, March 24, 2015"
output: pdf_document
classoption: landscape
---

``` {r echo=FALSE, warning=FALSE}
library("ggplot2")
library("reshape")
library("scales")
library("ggthemes")
library("knitr")
sc <- read.csv (file="scorecard_data.csv")
sc$Date <- as.Date(sc$Date, "%m/%d/%Y")
sc$PDate <- as.POSIXct(sc$Date)

data <- melt (sc, id=c("Date", "Year", "Month", "PDate"))
data$variable <- gsub("_", " ", data$variable)

mrr_data <- subset(data, variable == "MRR Sold" | variable == "MRR Completed" | variable == "MRR Plan")
budget_data <- subset(data, variable == "Expense Budget Original" | variable == "Expense Actual" | variable == "Expense Budget Latest")
conn_data <- subset(data, variable == "Connections Sold" | variable == "Connections Completed" | variable == "Connections Plan")

# prepare YTD data
sc_ytd <- subset(sc, Year == 2015)
sc_ytd <- cbind (sc_ytd, Cum_MRR_Comp=cumsum(sc_ytd$MRR_Completed))
sc_ytd <- cbind (sc_ytd, Cum_MRR_Sold=cumsum(sc_ytd$MRR_Sold))
sc_ytd <- cbind (sc_ytd, Cum_MRR_Plan=cumsum(sc_ytd$MRR_Plan))
sc_ytd <- cbind (sc_ytd, Cum_Conn_Comp=cumsum(sc_ytd$Connections_Completed))
sc_ytd <- cbind (sc_ytd, Cum_Conn_Sold=cumsum(sc_ytd$Connections_Sold))
sc_ytd <- cbind (sc_ytd, Cum_Conn_Plan=cumsum(sc_ytd$Connections_Plan))

data_ytd <- melt (sc_ytd, id=c("Date", "Year", "Month", "PDate"))
data_ytd$variable <- gsub("_", " ", data_ytd$variable)

mrr_data_ytd <- subset(data_ytd, variable == "Cum MRR Comp" | variable == "Cum MRR Sold" | variable == "Cum MRR Plan")
conn_data_ytd <- subset(data_ytd, variable == "Cum Conn Comp" | variable == "Cum Conn Sold" | variable == "Cum Conn Plan")


```


##Budget Notes:
* Delayed hiring has created the YTD positive variance
* Contractor working on PVH Latitude / Longitude in March
* Delayed hiring of some roles to Q3 to solve for "Q2 budget challenge"

```{r fig.width=10, echo=FALSE, warning=FALSE}
# create plot, add lines and points
g <- ggplot(data=budget_data, aes(x=PDate, y=value, group=variable)) 
g <- g + geom_line(aes(color=variable, group=variable)) 
g <- g + geom_point()  

# configure labels and axis
g <- g + ggtitle("Expense Budget vs Actual by Month") 
g <- g + xlab("Month") + ylab("Implementation Expenses") 
g <- g + scale_y_continuous(labels = dollar) 
g <- g + scale_x_datetime() 

# apply theme
g <- g + theme_few()

# blank out the legend title
g <- g+ theme(legend.title=element_blank(), legend.position="bottom") 


# add a vertical line on "today"
g <- g + geom_vline(lty="dotted", xintercept = as.numeric(Sys.time()))
g
```

\pagebreak

##MRR Notes:
* Excellent throughput in February, nearly a record
* Kate Spade and North Face were the largest implementations
* Pet Supplies Plus will complete in April which will drive MRR and connections

```{r fig.width = 10, echo=FALSE, warning=FALSE}
# create plot, add lines and points
g <- ggplot(data=mrr_data, aes(x=PDate, y=value, group=variable)) 
g <- g + geom_line(aes(color=variable, group=variable)) 
g <- g + geom_point()  

# configure labels and axis
g <- g + ggtitle("MRR Sold vs Completed vs Plan by Month") 
g <- g + xlab("Month") + ylab("MRR") 
g <- g + scale_y_continuous(labels = dollar) 
g <- g + scale_x_datetime() 

# apply theme
g <- g + theme_few()

# blank out the legend title
g <- g+ theme(legend.title=element_blank(), legend.position="bottom") 

# add a vertical line on "today"
g <- g + geom_vline(lty="dotted", xintercept = as.numeric(Sys.time()))
g

```


```{r echo=FALSE, warning=FALSE}

df <- data.frame(month=sc$Month, 
                 sc$MRR_Sold,
                 sc$MRR_Comp,
                 comp_to_sold=sc$MRR_Completed / sc$MRR_Sold,
                 sc$MRR_Plan, 
                 comp_to_plan=sc$MRR_Completed / sc$MRR_Plan)


df <- na.omit(df)

#format table
# percentages
df$comp_to_sold <- paste(format(round(df$comp_to_sold*100, digits=0), big.mark=","), "%")
df$comp_to_plan <- paste(format(round(df$comp_to_plan*100, digits=0), big.mark=","), "%")

#df$sc.Cum_MRR_Sold <- paste("$", format(round(df$sc.Cum_MRR_Sold, digits=0), big.mark=","))
df$sc.MRR_Plan <- paste("$", format(round(df$sc.MRR_Plan, digits=0), big.mark=","))
df$sc.MRR_Sold <- paste("$", format(round(df$sc.MRR_Sold, digits=0), big.mark=","))
df$sc.MRR_Comp <- paste("$", format(round(df$sc.MRR_Comp, digits=0), big.mark=","))
  
colnames(df) <- c("Month", "Sold", "Comp", "Comp to Sold", "Plan", "Comp to Plan")

kable(df)

```

\pagebreak

```{r fig.width = 10, echo=FALSE, warning=FALSE}

# create plot, add lines and points
g <- ggplot(data=mrr_data_ytd, aes(x=PDate, y=value, group=variable)) 
g <- g + geom_line(aes(color=variable, group=variable)) 
g <- g + geom_point()  

# configure labels and axis
g <- g + ggtitle("YTD Cumulative MRR Sold, Completed and Planned") 
g <- g + xlab("Month") + ylab("MRR") 
g <- g + scale_y_continuous(labels = dollar) 
g <- g + scale_x_datetime() 

# apply theme
g <- g + theme_few() 

# blank out the legend title
g <- g+ theme(legend.title=element_blank(), legend.position="bottom") 

# add a vertical line on "today"
g <- g + geom_vline(lty="dotted", xintercept = as.numeric(Sys.time()))
g
```

```{r echo=FALSE, warning=FALSE}

df <- data.frame(month=sc_ytd$Month, 
                 sc_ytd$Cum_MRR_Sold,
                 sc_ytd$Cum_MRR_Comp,
                 comp_to_sold=sc_ytd$Cum_MRR_Comp / sc_ytd$Cum_MRR_Sold,
                 sc_ytd$Cum_MRR_Plan, 
                 comp_to_plan=sc_ytd$Cum_MRR_Comp / sc_ytd$Cum_MRR_Plan)


df <- na.omit(df)

#format table
# percentages
df$comp_to_sold <- paste(format(round(df$comp_to_sold*100, digits=0), big.mark=","), "%")
df$comp_to_plan <- paste(format(round(df$comp_to_plan*100, digits=0), big.mark=","), "%")

#df$sc.Cum_MRR_Sold <- paste("$", format(round(df$sc.Cum_MRR_Sold, digits=0), big.mark=","))
df$sc_ytd.Cum_MRR_Plan <- paste("$", format(round(df$sc_ytd.Cum_MRR_Plan, digits=0), big.mark=","))
df$sc_ytd.Cum_MRR_Sold <- paste("$", format(round(df$sc_ytd.Cum_MRR_Sold, digits=0), big.mark=","))
df$sc_ytd.Cum_MRR_Comp <- paste("$", format(round(df$sc_ytd.Cum_MRR_Comp, digits=0), big.mark=","))
  
colnames(df) <- c("Month", "Sold", "Comp", "Comp to Sold", "Plan", "Comp to Plan")

kable(df)

```

\pagebreak

##Connection Notes:
* Pet Supplies Plus will complete in April which will drive MRR and connections


```{r fig.width = 10, echo=FALSE, warning=FALSE}

# create plot, add lines and points
g <- ggplot(data=conn_data, aes(x=PDate, y=value, group=variable)) 
g <- g + geom_line(aes(color=variable, group=variable)) 
g <- g + geom_point()  

# configure labels and axis
g <- g + ggtitle("Connections Sold vs Completed vs Plan by Month") 
g <- g + xlab("Month") + ylab("Connections") 
g <- g + scale_y_continuous() 
g <- g + scale_x_datetime() 

# apply theme
g <- g + theme_few()

# blank out the legend title
g <- g+ theme(legend.title=element_blank(), legend.position="bottom") 

# add a vertical line on "today"
g <- g + geom_vline(lty="dotted", xintercept = as.numeric(Sys.time()))
g

```


```{r fig.width = 10, echo=FALSE, warning=FALSE}
df <- data.frame(month=sc$Month, 
                 sc$Connections_Sold,
                 sc$Connections_Completed,
                 comp_to_sold=sc$Connections_Completed / sc$Connections_Sold,
                 sc$Connections_Plan, 
                 comp_to_plan=sc$Connections_Completed / sc$Connections_Plan)

df <- na.omit(df)

#format table
# percentages
df$comp_to_sold <- paste(format(round(df$comp_to_sold*100, digits=0), big.mark=","), "%")
df$comp_to_plan <- paste(format(round(df$comp_to_plan*100, digits=0), big.mark=","), "%")

df$sc.Connections_Plan <- format(round(df$sc.Connections_Plan, digits=0), big.mark=",")
df$sc.Connections_Sold <- format(round(df$sc.Connections_Sold, digits=0), big.mark=",")
df$sc.Connections_Completed <- format(round(df$sc.Connections_Completed, digits=0), big.mark=",")
  
colnames(df) <- c("Month", "Sold", "Comp", "Comp to Sold", "Plan", "Comp to Plan")

kable(df)

```


```{r fig.width = 10, echo=FALSE, warning=FALSE}
#create plot, add lines and points
g <- ggplot(data=conn_data_ytd, aes(x=PDate, y=value, group=variable)) 
g <- g + geom_line(aes(color=variable, group=variable)) 
g <- g + geom_point()  

# configure labels and axis
g <- g + ggtitle("YTD Cumulative Connections Sold, Completed and Planned") 
g <- g + xlab("Month") + ylab("Connections") 
g <- g + scale_y_continuous() 
g <- g + scale_x_datetime() 

# apply theme
g <- g + theme_few() 

# blank out the legend title
g <- g+ theme(legend.title=element_blank(), legend.position="bottom") 

# add a vertical line on "today"
g <- g + geom_vline(lty="dotted", xintercept = as.numeric(Sys.time()))
g
```



```{r echo=FALSE, warning=FALSE}

df <- data.frame(month=sc_ytd$Month, 
                 sc_ytd$Cum_Conn_Sold,
                 sc_ytd$Cum_Conn_Comp,
                 comp_to_sold=sc_ytd$Cum_Conn_Comp / sc_ytd$Cum_Conn_Sold,
                 sc_ytd$Cum_Conn_Plan, 
                 comp_to_plan=sc_ytd$Cum_Conn_Comp / sc_ytd$Cum_Conn_Plan)


df <- na.omit(df)

#format table
# percentages
df$comp_to_sold <- paste(format(round(df$comp_to_sold*100, digits=0), big.mark=","), "%")
df$comp_to_plan <- paste(format(round(df$comp_to_plan*100, digits=0), big.mark=","), "%")

df$sc_ytd.Cum_Conn_Plan <- format(round(df$sc_ytd.Cum_Conn_Plan, digits=0), big.mark=",")
df$sc_ytd.Cum_Conn_Sold <- format(df$sc_ytd.Cum_Conn_Sold, big.mark=",")
df$sc_ytd.Cum_Conn_Comp <- format(df$sc_ytd.Cum_Conn_Comp, big.mark=",")
  
colnames(df) <- c("Month", "Sold", "Comp", "Comp to Sold", "Plan", "Comp to Plan")

kable(df)

```
